Strength, mating success, and immune and dietary costs in a population sample of US women and men: a registered report

### 2024-09-15 paper.qmd
Minor adjustment of heading levels and reorganization of the SI.

## Post Hoc Analyses
We were made aware that Dual-Energy X-ray Absorptiometry (DXA) data were published for these series after our initial download of the data for this study. DXA data provide alternatives to grip strength for assessing muscle mass, and include the lean masses (i.e., fat-free mass, optionally including or excluding bone mineral content) in grams of each arm and leg, the trunk, and total body. Total body lean mass is similar to the bioelectrical impedance analysis fat-free mass variable used by @lassek2009. For reviews of DXA measurements of body composition, see @shepherd2017 and @messina2020. For details of the NHANES DXA measurements, see @DXXG2023. In addition to our grip strength models, we also fit our models exactly as specified in stage 1 except substituting four DXA lean masses for grip strength (all masses excluded bone mineral content). Specifically, we computed arm lean mass as the sum of left and right arm lean masses, and leg lean mass as the sum of left and right leg lean masses. We then fit our models using arm, leg, trunk, and total lean masses, each standardized by sex as described earlier for grip strength.

@@

## Discussion

@@

## Conclusion

@@

@@

## Combined G and H series data (2011-2014)

@@

## Lean mass coefficient plots

### Arm lean mass

### Leg lean mass

### Trunk lean mass

### Total lean mass

>>>>

# Post Hoc Analyse

We were made aware that Dual-Energy X-ray Absorptiometry (DXA) data were published for these series after our initial download of the data for this study. DXA data provide alternatives to grip strength for assessing muscle mass, and include the lean masses (i.e., fat-free mass, optionally including or excluding bone mineral content) in grams of each arm and leg, the trunk, and total body. Total body lean mass is similar to the bioelectrical impedance analysis fat-free mass variable used by @lassek2009. For reviews of DXA measurements of body composition, see @shepherd2017 and @messina2020. For details of the NHANES DXA measurements, see @DXXG2023. In addition to our grip strength models, we also fit our models exactly as specified in stage 1 except substituting four DXA lean masses for grip strength (all masses excluded bone mineral content). Specifically, we computed arm lean mass as the sum of left and right arm lean masses, and leg lean mass as the sum of left and right leg lean masses. We then fit our models using arm, leg, trunk, and total lean masses, each standardized by sex as described earlier for grip strength.

@@

Finally, we fit our grip strength models on the combined data (2011-2014). Results qualitatively correspond to those seen in the pilot study, which is not surprising because our models were developed on the pilot data. See @sfig-matingGH - @sfig-intakeGH.

# Discussion

@@

# Conclusion

@@

## Post hoc results

### Lean mass coefficient plots

#### Arm lean mass

#### Leg lean mass

#### Trunk lean mass

#### Total lean mass

@@

### Combined G and H series data (2011-2014)

@@
